\chapter{Appendix 2 - User documentation}
We provide source codes of bots and all small tools we developed during our
work. All is available in \url{http://github.com/JackeLee/rabbocop} or on
included CD.

\section{Compiling options}
Source codes of programs are saved on CD in \texttt{rabbocop} dictionary.
We use the make for building our programs. Simple writing \texttt{make
IterativeAB} or \texttt{make MCTS} compiles either AlphaBeta or MCTS in its
standart version of the bot.


\begin{description}
\item[VERBOSE=$n$]{
	For IterativeAB program, this will print actual best move and score anytime
	a depth is fully explored.
	For MCTS it will print actual best move and score after each $n$ iterations of
	UCT algorithm.
	}

\item[EVAL=fairy]{
	Builds program using Fairy's evaluation function.}

\item[NULL\_MOVE]{
	Enables Null moves for AlphaBeta search.}

\item[canPass=1]{
	Adds possibility to generate less than 4 moves.}

\item[CORES=$X$]{
	Compiles program with the number of available CPU's set to $X$. (Default is 1)
	When running program compiled with CORES=X it is necessary to add +RTS -N$X$
	as additional arguments.}

\item[WINDOW=$X$]{
	It switches on aspiration window option for AlphaBeta algorithm with Window
	set to $X$.}

\item[noHH=1]{
	Disables history heuristics optimisations for MCTS.}

\item[abHH=1]{
	Enables history heuristics optimisations for AlphaBeta.}

\item[noHeavyPlayout=1]{
	This disables heuristic in playouts.}

\item[PROF=1]{
	Enables profiling for bots.}

\item[playAB, playMCTS, or playMatch]{
	Starts new game to play by human vs AlphaBeta search, human versus MCTS or
	AlphaBeta search versus MCT.
	For the first time it downloads testing and graphical environments for
	offline matches.
	}
\end{description}
