\def\bibname{Literature}
\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{\bibname}

\bibitem{KOZELEK}
	{\sc KOZELEK,} Tomáš.
	\emph{MCTS methods in the game of Arimaa}.
	Master's thesis.
	Charles University in Prague, 2009.

\bibitem{COX}
	{\sc COX,} Christ-Jan.
	\emph{Analysis and Implementation of the Game Arimaa}.
	Master Thesis.
	Universiteit Maastricht, 2006.

\bibitem{arimaa.com}
	Arimaa homepage.
	\url{http://arimaa.com/}.

\bibitem{syed}
	{\sc SYED,} Omar, and {\sc SYED,} Aamir.
	\emph{Arimaa: A New Game Designed to be Difficult for Computers}.
	Journal of the International Computer Games Association, 26(2):138--139, 2003.

\bibitem{knuth:alphabeta}
	{\sc KNUTH,} Donald E., and {\sc MOORE,} R. W..
	\emph{An Analysis of Alpha-Beta Pruning}.
	Artificial Intelligence Vol. 6, No. 4: 293--326, 1975. Reprinted in Selected
	Papers on Analysis of Algorithms by Donald E. Knuth. Addison-Wesley, 2000.
	ISBN: 1-57585-211-5.

\bibitem{ZHONG}
	{\sc ZHONG,} Haizhi.
	\emph{Building a Strong Arimaa-playing Program}.
	Master Thesis.
	University of Alberta, 2005.

\bibitem{progressive-strategies}
	{\sc CHASLOT,} Guillaume, {\sc WINANDS,} Mark, {\sc HERIK,} Jaap H. van den,
	{\sc UITERWIJK,} Jos, and {\sc BOUZY,} Bruno.
	\emph{Progressive strategies for Monte-Carlo tree search}.
	In Joint Conference on Information Sciences, Salt Lake City 2007, Heuristic
	Search and Computer Game Playing Session, 2007.

\bibitem{BERND}
	{\sc BERND,} Brugmann.
	\emph{Monte carlo go}.
	Technical report, 1993.

\bibitem{MonteCarloMethod}
	{\sc METROPOLIS,} N.
	\emph{The beginning of the Monte Carlo method}.
	Los Alamos Science (1987 Special Issue dedicated to Stanisław Ulam):
	125--130, 1987.

\bibitem{MonteCarloGo}
	{\sc BOUZY,} B., {\sc HELMSTETTER,} B.
	\emph{Monte-Carlo Go Development}.
	Advances in Computer Games 10, 2003.

\bibitem{MoGo}
	{\sc GELLY,} Sylvain, {\sc WANG,} Yizao.
	\emph{Exploration exploitation in Go: UCT for Monte-Carlo Go}.
	University of Paris-Sud, 2006.

\bibitem{MultiarmedBandit}
	{\sc AURER,} Peter , {\sc CESA-BIANCHI,} Nicol`, and {\sc FISCHER,} Paul.
	\emph{Finite-time analysis of the o multiarmed bandit problem}.
	Mach. Learn., 47(2--3):235--256, 2002.

\bibitem{HeavyPlayouts}
	{\sc DRAKE,} Peter, and {\sc UURTAMO,} Steve.
	\emph{Move ordering vs heavy playouts: Where should heuristics be applied
	in Monte Carlo Go}?
	In Proceedings of the 3rd North American Game-On Conference, 2007.

\bibitem{PatternsGo}
	{\sc GELLY,} Sylvain, {\sc WANG,} Yizao, {\sc MUNOS,} R'mi, and {\sc
	TEYTAUD,} Olivier.
	\emph{Modification of UCT with patterns in Monte-Carlo Go}.
	Technical Report 6062, INRIA, France, November 2006.

\bibitem{PatternsArimaa}
	{\sc TRIPPEN,} Gerhard.
	\emph{Plans, Patterns and Move Categories Guiding a Highly Selective Search}.
	The University of British Columbia, 2009.

\bibitem{WorldChampion}
	{\sc Fotland,} David.
	\emph{Building a World Champion Arimaa Program}.
	CG 2004, LNCS 3846 (2006) 175--186.

\bibitem{BitboardAnalysis}
	{\sc CARLINI,} Stefano.
	\emph{Arimaa: from rules to bitboard analysys}.
	Knowledge Representation Thesis.
	University of Modena and Reggio Emilia, 2008.

\bibitem{UCTanalysis}
	{\sc KOCSIS,} Levente, {\sc SZEPESVÁR,} Csaba, and {\sc WILLEMSON,} Jan.
	\emph{Improved Monte-Carlo Search}.
	University of Tartu, 2006.

\bibitem{AspirationWindow}
	{\sc Shams,} Reza, {\sc KAINDL,} Hermann, and {\sc HORACEK,} Helmut.
	\emph{Using aspiration windows for minimax algorithms}.
	In Procs. 8th Int. Joint Conf. on Art. Intell, 192--197, Kaufman, 1991.

\end{thebibliography}

