\chapter{Preliminaries}
In this chapter we present a summary of all relevant and well--known facts to point--free topological which we will need in the following chapters.

We assume the reader has a basic knowledge of Set Theory, mainly that he knows basic facts about cardinal numbers, cardinalities and Axiom of Choice.
We refer to the monograph \emph{Frames and Locales} written by Pultr and Picado~\cite{picado2011frames} as an introduction to point--free topology.

\subsubsection*{A few comments on notation}
For sets $X,Y$ and a mapping $f\colon X\to Y$, denote $f[S] = \Set{ f(s) | s\in S}$ and $f^{-1}[M] = \Set{ x\in X | f(x)\in M}$ for any subsets $S\subseteq X$ and $M\subseteq Y$.
$[0,1]$ is the closed interval of real numbers greater than or equal to 0 and less than or equal to 1, similarly, $[0,\infty)$ is the set of all non-negative real numbers.

We will often denote a mathematical structure, such as lattice, topological space, frame etc., by the same symbol as we use for its underlying set.
In expressions, the rightmost unary operation is applied first. For example $\downset \bigvee_i a_i^*$ is the same as $\downset \left(\bigvee_i (a_i^*)\right)$.

\section{Partially ordered set}

\num Let $A$ be a set and let $\leq$ be a binary relation on $A$ ($(\leq) \subseteq A\times A$). We say that $(A, \leq)$ is a \DEF{partially ordered set} if the relation $\leq$ is \emph{partial order}, i.e. satisfies:
\begin{enumerate}[(P1)]
    \item \emph{reflexivity:} $a \leq a$ for all $a \in A$,
    \item \emph{antisymmetry:} $a \leq b$ and $b\leq a$ implies $a = b$ for all $a,b \in A$,
    \item \emph{transitivity:} $a \leq b$ and $b\leq c$ implies $a \leq c$ for all $a,b,c \in A$.
\end{enumerate}

A partially ordered set $(A,\leq)$ is said to be \emph{with 1} or \emph{with the top} (resp. \emph{with 0} or \emph{with the bottom}) if $1\in A$ (resp. $0\in A$) and $1\geq a$ (resp. $0\leq x$) for all $a\in A$.
A partially ordered set is said to be \emph{bounded} if it is both with 0 and with 1.
Denote by $(A,\leq)\op$ the partially ordered set $(A,\leq')$ where $(\leq') = \Set{ (b,a) \in A\times A | a\leq b}$.

Let $S$ be a subset of $A$.
We say that $u$ is an \emph{upper bound} of $S$ if $u \geq x$ for all $x\in S$. We say that $s$ is a \emph{supremum} of $S$, and we write $s = \bigvee S$, if $s$ is the least upper bound of $S$.
We say that $l$ is an \emph{lower bound} or an \emph{infimum} if $l$ is an upper bound or the supremum of $S$ in $A\op$.

A partially ordered set $(A,\leq)$ is \emph{join--semilattice} if every two element subset has a supremum. Similarly, \emph{meet--semilattice} has an infimum for every two element subset.
A \DEF{lattice} is partially ordered set which is both join-- and meet--semilattice. We write $a\vee b$ for the supreum (the \emph{meet}) of $\{a,b\}$ and $a\wedge b$ for the infimum (the \emph{join}).

A mapping $f\colon A\to B$ between two partially ordered sets is called \emph{monotone} if $f(x)\leq f(y)$ wherever $x\leq y$. If, moreover, $A$ and $B$ are lattices and $f(x\vee y) = f(x)\vee f(y)$ and $f(x\wedge y) = f(x)\wedge f(y)$ for all $x,y\in A$, we say that $f$ is a \emph{lattice homomorphism}.

\num A lattice is called a \DEF{complete lattice} if each of its subsets has an infimum and a supremum.

\begin{proposition*}
    For a lattice $L$ are the following conditions equivalent:
    \begin{itemize}
        \item $L$ is a complete lattice;
        \item every subset of $L$ has a supremum;
        \item every subset of $L$ has an infimum.
    \end{itemize}
\end{proposition*}

For a complete lattice we therefore have two infinitary operations the meet $\bigvee$ and the join $\bigwedge$.
Note that every complete lattice is bounded, $0 = \bigvee \emptyset = \bigwedge L$ and $1 = \bigwedge \emptyset = \bigvee L$.

A lattice homomorphism $f\colon A\to B$ between two complete lattices is a \DEF{complete lattice homomorphism} if $f(\bigvee X) = \bigvee f[X]$ and $f(\bigwedge X) = \bigwedge f[X]$ for each subset $X \subseteq A$.

\num A lattice $D$ is \DEF{distributive} if the following equation holds for all $a,b,c\in D$:
\begin{align*}
    a\vee (b\wedge c) = (a\vee b)\wedge (a\vee c).
\end{align*}

\begin{proposition*}
    For a lattice $L$, the following conditions are equivalent:
    \begin{itemize}
        \item $L$ is a distributive lattice,
        \item $a\vee (b\wedge c) = (a\vee b)\wedge (a\vee c)$ for all $a,b,c \in L$,
        \item For each $a,b,c\in L$ there exists at most one $x\in L$ such that
            \begin{align*}
                a\vee x &= b\\
                a\wedge x &= c.
            \end{align*}
    \end{itemize}
\end{proposition*}

\num Let $A$ and $B$ be two partially ordered sets. Two monotone mappings $f\colon A \to B$ and $g\colon B\to A$ are in \DEF{Galois connection} or are \DEF{Galois adjoing} if
$$ f(x) \leq y\quad\text{iff}\quad x\leq g(y)\quad\text{for all } x\in A, y\in B.$$

\noindent Or equivalently
$$ fg(y) \leq y\quad\text{and}\quad x\leq gf(y)\quad\text{for all } x\in A, y\in B.$$

Then, we say that $f$ is a left Galois adjoing of $g$ and the $g$ is a right Galois adjoing of $f$.
For a monotone map $f$, its left or right Galois adjoint do not need to exists but if it does, it is uniquely determined. We will write $f^*$ for the right adjoint and $f_*$ for the left adjoint.

For two monotone maps in Galois connection $f,g$ we have that
$$ f g f = f\quad\text{and}\quad g f g = g. $$

\begin{proposition*}
    For a monotone map $f\colon A\to B$, if $f$ is a left (resp. right) Galois adjoint
    then $f$ preserves all existing suprema (resp. infima).

    Moreover, the converse implication also holds if $A$ and $B$ are complete lattices.
\end{proposition*}

\num Let $L$ be a lattice with 0. A \emph{pseudocomplement} $a^*$ for an element $a\in L$ is the greatest element $x$ such that
$$ x\wedge a = 0. $$

\noindent Equivalently, $a^*$ is the pseudocomplement of $a$ if
$$ x\wedge a = 0 \quad\text{iff}\quad x\leq a^*\quad\text{for all } x\in L. $$

A lattice is called \DEF{pseudocomplemented}[ lattice] if every element has a pseudocomplement. Pseudocomplements, if exist, satisfy the following properties:

\begin{enumerate}\label{p:pseudcomplProperties}
    \item $a \leq a^{**}$,
    \item $a^* = a^{***}$,
    \item $a \leq b$ implies $a^* \geq b^*$,
    \item $(a \wedge b)^{**} = a^{**} \wedge b^{**}$.
\end{enumerate}

\num Let $L$ be a meet semilattice with 0 and with a binary operation $\to$, $L$ is said to be a \DEF{Heyting algebra} if the following holds
$$ a\wedge x\leq b\quad\text{iff}\quad a\leq x\to b\quad\text{for all } a,b,x\in L.$$

Note that each Heyting algebra is pseudocomplemented semilattice with pseudocomplements defined
$$ a^* = a\to 0.$$

From the definition we see that the operation $x\to (-)$ is the right Galois adjoint to $(-) \wedge x$.
Therefore, each meet semilattice admits at most one Heyting operation.

\begin{proposition*}
    Let $H$ be a Heyting algebra, then
    $$ (\bigvee_i a_i)^* = \bigwedge_i a_i^*$$
    holds whenever $\bigvee_i a_i$ exists.
\end{proposition*}

\begin{proposition*}
    A complete lattice admits a Heyting operation iff the following equation holds
    $$ (\bigvee_i a_i)\wedge b = \bigvee_i (a_i\wedge b)\quad\text{for all } a_i, b. $$
\end{proposition*}

\num Let $B$ be a bounded distributive lattice, we say that $B$ is a \DEF{Boolean algebra} if for every element $a\in B$ there exists a (\emph{complement}) $a^c\in B$ such that
$$ a\vee a^c = 1\quad\text{and}\quad a\wedge a^c=0. $$

Since $B$ is a distributive lattice, such $a^c$ is uniquely determined. Each Boolean algebra is a Heyting algebra with the Heyting operation defined as follows
$$ a\to b = a^c\vee b.$$
Hence, it is also a pseudocomplemented lattice with pseudocomplements equal to complements.

Let $f$ be a lattice homomorphism between two Boolean algebras, $f$ is said to be a \DEF{Boolean homomorphisms} if $f$ preserves 0 and 1.
The following equations holds for any Boolean algebra
$$ (\bigvee_i a_i)^c = \bigwedge_i a_i^c\quad\text{resp.}\quad (\bigwedge_i a_i)^c = \bigvee_i a_i^c,$$
whenever $\bigvee_i a_i$ resp. $\bigwedge_i a_i$ exists.

\num Let $L$ be a bounded distributive lattice, then a subset $F\subseteq L$ is a \DEF{filter} if
\begin{enumerate}[(F1)]
    \item $0\not\in F$ and $1\in F$,
    \item $a\in F$ and $a\leq b\in L$ implies $b\in F$, and
    \item $a,b\in F$ implies $a\wedge b\in F$.
\end{enumerate}

Similarly, an ideal is a subset $I\subseteq L$ such that
\begin{enumerate}[(I1)]
    \item $1\not\in I$ and $0\in I$,
    \item $a\in I$ and $a\geq b\in L$ implies $b\in I$, and
    \item $a,b\in I$ implies $a\vee b\in I$.
\end{enumerate}

A filter $F\subseteq L$ is called \DEF{prime filter} if $a\vee b\in F$ implies $a\in F$ or $b\in F$.
$F$ is called \DEF{completely prime filter} if $\bigvee A\in F$ implies $a\in F$ for some $a\in A$.
A \DEF{principal filter} is any filter of $L$ of the form $\upset a = \Set{ x | x\geq a}$ for some $a$.

Similarly, an ideal $I$ is called \DEF{prime ideal}, \DEF{completely prime ideal} or \DEF{principal ideal} if $I$ is a prime filter, completely prime filter or principal filter of $L\op$.
Principal ideals will be denoted by $\downset a = \Set{ x | x\leq a}$ for some $a$.

\begin{proposition*}
    Let $B$ be a Boolean algebra and a filter $F\subseteq B$. Then the following are equivalent
    \begin{itemize}
        \item $F$ is a maximal filter,
        \item $F$ is a prime filter.
        \item For every $b\in B$, either $b\in F$ or $b^c\in F$.
    \end{itemize}
\end{proposition*}

From the Proposition we see that the definition of a maximal filter and a prime filter coincide for Boolean algebras, hence we call such filter simply \DEF{ultrafilter}.

% TODO say something
\num When we refer to \DEF{Axiom of Choice}, we usually refer to its equivalent form -- Zorn's Lemma:
\begin{center}\em
    \DEF{(AC)}\quad Let $X$ be a non-empty partially ordered set such that every non-empty chain has an upper bound, then $X$ has at least one maximal element.
\end{center}

\noindent By \DEF{Boolean Ultrafilter Theorem} we mean the following choice principle
\begin{center}\em
    \DEF{(BUT)}\quad Let $B$ be a Boolean algebra and let $F$ be a filter of $B$, then there exists a prime filter extending $F$.
\end{center}

\noindent Which is equivalent to
\begin{center}\em
    \emph{(BUT')}\quad Let $B$ be a Boolean algebra and let $F$ be a filter and let $I$ be an ideal of $B$ such that $F\cap I = \emptyset$, then there exists a prime filter $G$ extending $F$ such that still $G\cap I=\emptyset$.
\end{center}

\noindent Finally, the last choice principle we will need to know is \DEF{Axiom of Countable Dependent Choice}
\begin{center}\em
    \DEF{(CDC)}\quad Let $R$ be a binary relation on a set $X$ such that for every $a\in X$ there exists $b\in X$ satisfying $aRb$, then there exist a countable sequence $(a_i)_{i=1}^\infty$ such that $a_iRa_{i+1}$ for all $i=1,2,\dots$.
\end{center}

Axiom of Choice is stronger than Boolean Ultrafilter Theorem or Axiom of Countable Dependent Choice, it logically implies both of them.

\section{Category Theory}
\num A category $\p C$ is a class of objects ($\obj \p C$), a class of morphisms ($\morph \p C$) and two mappings $\dom,\codom\colon \morph\p C\to \obj\p C$ (\emph{domain} and \emph{codomain}) satisfying conditions (C1)--(C3) bellow.

Notation: For a morphism $f\in \morph \p C$, we write $f\colon A\to B$ or $A \stackrel{f}{\to} B$ whenever we want to highlight the fact that $A = \dom(f)$ and $B = \codom(f)$.

\begin{enumerate}[(C1)]
    \item Let $f\colon A\to B, g\colon B\to C$ be two morphisms of $\p C$, then there exists their \emph{composition}, the morphism $g\cdot f\colon A\to C$.
    \item Morphism composition satisfies the \emph{associativity law}: $(f\cdot g)\cdot h = f\cdot (g\cdot h)$ whenever are the composition defined.
    \item For each object $A\in \obj \p C$ there exists an \emph{identity morphism} $1_A$ satisfying $1_A\cdot f = f$ and $g\cdot 1_A = g$ whenever are the compositions defined.
\end{enumerate}

We say that a category is \emph{small} if $\morph \p C$ is a set.
A \emph{dual category} $\p C\op$ of a category $\p C$ is the category with the same class of objects as $\p C$ has and with all morphisms of $\p C$ reversed, i.e. for each morphism $f\colon A\to B\in \morph \p C$, $\hat f\colon B\to A$ is a morphism of $\p C\op$. The composition $\diamond$ of $\p C\op$ is defined as
$$ \hat f\diamond \hat g = \widehat{g\cdot f}. $$

To simplify the notation, we will write $f g$ instead of $f\cdot g$, $A\in \p C$ instead of $A\in \obj \p C$ and similarly for $\morph$, whenever there is no danger of confusion.

\begin{block*}{Examples}
    The most natural example of a category is the category $\categoryStyle{Set}$ of all sets, all maps between them and composition defined as map composition.

    An important example is the category \DEF{\Bool} of all Boolean algeras and all Boolean homomorphisms. Also, an arbitrary partially ordered set $(X,\leq)$ is a category with the set $X$ as objects and one morphism between $x,y\in X$ whenever $x\leq y$ (composition holds thanks to transitivity of $\leq$).

    Observe that the dual category of $(X,\leq)$ is precisely the category $(X,\leq)\op$.
\end{block*}

\num A morphism $f$ is a \emph{monomorphism} whenever $fg = fh$ implies $g = h$. Analogously, $f$ is an \emph{epimorphism} if $gf = hf$ implies $g = h$. Finally, $f$ is an \emph{isomorphism} if there exists a $f^{-1}$ such that
$$ f\cdot f^{-1} = 1\quad\text{and}\quad f^{-1}\cdot f = 1.$$

If $fg = 1$, then $f$ is an epimorphism and $g$ is a monomorphism.

\num For categories $\p C, \p D$ the mappings $F\colon \obj \p C\to \obj \p D$ and $F\colon \morph \p C\to \morph\p D$ constitute a \emph{(covariant) functor} if
$$ F(f)\colon F(A)\to F(B)\quad\text{for any }f\colon A\to B\in \morph\p C, $$
$$ F(1_A) = 1_{F(A)}\quad\text{for any }A \in \obj \p C,\quad\text{and}\quad F(gh)=F(g)F(h).$$

\begin{block*}{Examples}
    Let $\p C$ be a category, the \DEF{identity functor} on $\p C$ is defined by the mappings
    $$\Id_{\p C}(A) = A\colon \obj\p C\to \obj\p C,\quad\text{and}\quad \Id_{\p C}(f) = f\colon \morph\p C\to \morph\p C.$$

    Let $\p D$ be a non-empty category and let $T$ be an object of $\p D$, then the \emph{constant functor} is defined as follows
    $$K(A)=T\quad\text{and}\quad K(f)=1_T\quad\text{for all } A,f\in \p C.$$
\end{block*}

We say that a functor is \DEF{contravariant}[ functor] if it is of the form $F\colon \p C\to \p D\op$. The composition of functors $F\colon \p C\to \p D$ and $G\colon \p D\to \p E$ is denoted by $G\circ F\colon \p C\to \p E$or simply $GF$.

\num Let $F,G\colon \p C\to \p D$ be two functors, a collection of morphisms $m_* = (m_A)_{A\in \obj\p C}$ is a \emph{natural transformation} between $F$ and $G$, $m_*\colon F\natto G$, if
$$ m_A\colon F(A)\to G(A),\quad\text{for all } A\in \obj\p C, $$

% TODO first use of the word ``diagram'', it should be explained
\noindent and the following diagram commutes
\begin{diagram}
    F(A)\ar{r}{m_A}\ar{d}{F(f)} & G(A)\ar{d}{G(f)}\\
    F(B)\ar{r}{m_B} & G(B)
\end{diagram}
for all $f\colon A\to B$, morphisms of $\p C$.

If a natural transformation $m_*$ is a collection of isomorphism, we say that $m_*$ is a \emph{natural equivalence}. For two functors $F$ and $G$, if there exists a natural equivalence $m_*\colon F\natto G$, we say that $F$ and $G$ are \emph{naturally equivalent} and write $F\cong G$.

\begin{block*}{Example}
    For a functor $F\colon \p C\to \p D$, the collection of morphisms $(1_{F(A)})_{A\in \p C}$ is an \emph{identity natural transformation} $F\natto F$.
\end{block*}

\num A \emph{limit} of a \emph{diagram} $D$ in the category $\p C$ (that is, of a functor $D\colon \p D\to \p C$ for a small category $\p D$) is a constant functor $L\colon \p D\to \p C$ and a natural transformation $l_*\colon L\natto D$ satisfying universal property.

In other words, $l_*$ is such that for any constant functor $K\colon \p D\to \p C$ and a natural transformation $k_*\colon K\natto D$ there exists an unique natural transformation $m_*\colon K\natto L$ such that the following diagram commutes
\begin{diagram}
    L\ar{r}{l_*} & D\\
    K\ar[dashed]{u}{m_*}\ar{ur}{k_*} &
\end{diagram}

\noindent (in the category $[\p D,\p C]$ of all functors from $\p D$ to $\p C$ and natural transformations as morphisms). From the definition, we see that limits are determined uniquely up to isomorphisms.

A \emph{colimit} is defined dually to limit, that is, a colimit of a diagram $D$ is the limit of $D$ in the category $\p C\op$.
A category is said to be \emph{(co)complete} if there is a (co)limit for every diagram.

\begin{block*}{Examples}
    A well--known example of a limit in \categoryStyle{Set} is the (cartesian) product of sets $\prod_{i\in I} X_i$ together with projections $(\prod_{i\in I} X_i\to X_j)_{j\in I}$.

    Similarly, a natural example of colimit in \categoryStyle{Set} is the coproduct, the disjoint union, of sets $\coprod_{i\in I} X_i$ together with injections $(X_j\to \coprod_{i\in I} X_i)_{j\in I}$.
\end{block*}

\num Functors $F\colon \p C\to \p D$ and $G\colon \p D\to \p C$ are \emph{adjoint} (with $F$ on the left and $G$ on the right) if there exist \emph{units of adjuction}, that is, natural transformations (\emph{an unit and a counit})
$$ \lambda_*\colon FG\natto \Id_{\p D}\quad\text{and}\quad \rho_*\colon \Id_{\p C}\natto GF,$$

\noindent such that the following compositions of natural transformations
$$ F\xrightarrow{~F(\rho_*)~} FGF\xrightarrow{~\lambda_{F(*)}~} F\quad\text{and}\quad G\xrightarrow{~\rho_{G(*)}~} GFG\xrightarrow{~G(\lambda_*)~} G$$

\noindent are equal to identity natural transformations on $F$ and on $G$, or more precisely: $F(\rho_A)\cdot \lambda_{F(A)} = 1_{F(A)}$ and $\rho_{G(B)}\cdot G(\lambda_B) = 1_{F(B)}$ for all $A\in\p C$ and $B\in\p D$.

\begin{proposition*}
    Right adjoinits preserve limits and left adjoinits preserve colimits.
\end{proposition*}

Two categories $\p C,\p D$ are said to be \emph{isomorphic}, and we write $\p C\cong \p D$, if there exists adjoint functors $F\colon \p C\to \p D$ and $G\colon \p D\to \p C$ with units of adjunction consisting of natural equivalences.

\num A category $\p C$ is said to be \emph{subcategory} of a category $\p D$ if $\obj\p C\subseteq \obj\p D$, $\morph\p C\subseteq \morph\p D$ and the composition of morphisms in $\p C$ coincide with that in $\p D$. Moreover, if $\Set{f | f\colon A\to B\in \p C} = \Set{f | f\colon A\to B\in \p D}$ for every $A, B\in \obj\p C$, we say that $\p C$ is a \emph{full subcategory} of $\p D$.

A full subcategory $\p C$ of a category $\p D$ is \emph{reflexive} (or \emph{coreflexive}) if the embedding functor $J\colon \p C\xrightarrow{~\subseteq~} \p D$ is a right (or left) adjoint.

\begin{block*}{Example}
    The category \Bool{} is reflexive subcategory of the category of bounded distributive lattices and lattice homomorphisms.
\end{block*}

\begin{proposition*}
    Each reflexive subcategory of a (co)complete category is (co)complete. Similarly for coreflexive categories.
\end{proposition*}

\section{Topology and point--free Topology}

\num Let $X$ be a set and $\tau$ an arbitrary set of subsets of $X$, then the pair $(X,\tau)$ is a \emph{topological space} if
\begin{enumerate}[(T1)]
    \item $\emptyset, X \in \tau$,
    \item $\p M \subseteq \tau$ implies $\bigcup \p M \in \tau$, and
    \item for $U, V \in \tau$, also $U\cap V\in \tau$.
\end{enumerate}

A subset of $X$ which is also an elements of $\tau$ is called \emph{open} and the complement of an open set is called \emph{closed}. A subset of $X$ is said to be \emph{clopen} if it is both open and closed.
\emph{The closure} of a set is the least closed set containing it.

Let $(X,\tau), (Y,\sigma)$ be topological spaces and a mapping $f\colon X\to Y$ is said to be \emph{continuous (with respect to $\tau$ and $\sigma$)} if
$$ f^{-1}[O] \in \tau,\quad\text{for all } O\in \sigma.$$

\noindent Denote by \Top{} the category of all topological spaces and continuous mappings. Isomorphisms of \Top{} are called \emph{homeomorphisms}.

As we see from the conditions (T1)--(T3), the set $\tau$ ordered by inclusion is a complete lattice. Moreover, we have $(\bigcup_i U_i)\cap V = \bigcup_i (U_i\cap V)$ for $U_i, V\in \tau$.
Therefore, we can generalize the notion of topological space:

Let $L$ be a complete lattice, we say that $L$ is a \DEF{frame} if
$$ (\bigvee A)\wedge b = \bigvee_{a\in A} ( a\wedge b ) $$
for any $A\subseteq L$ and $b\in L$. We see that frames are just complete Heyting algebras and, consequently, pseudocomplemented lattices.
The pseudocomplements are given by the following formula
$$ a^* = \bigvee \Set{ x | x\wedge a = 0}. $$

\noindent For an open set of some space, taking pseudocomplements in the corresponding frame of open sets is the same as taking the interior of the complement.

Let $L$ and $M$ be frames and $f\colon L\to M$ a monotone map, $f$ is said to be a \DEF{frame homomorphism} if $f$ preserves all joins, finite meets, the top and the bottom (1 and 0).
Denote by \Frm{} the resulting category of all frames and frame homomorphisms.

We have the obvious (contravariant) functor $\Omega\colon \Top\to \Frm$
$$ \Omega(X,\tau) = \tau\quad\text{and}\quad \Omega(f)\colon U\mapsto f^{-1}[U],$$
for $(X,\tau), f \in \Top$.

A frame homomorphism $f$ is monotone mapping between complete lattices which preserves all suprema. Hence, it has the right adjoint $f^*$, a \emph{localic map}.
Denote the category of frames and localic maps as morphisms by $\Loc$. We will refer to objects of $\Loc$ as \emph{locales}. Trivially $\Loc\cong\Frm\op$.

Again, we have a functor $\Lc\colon \Top\to \Loc$ (covariant this time)
$$ \Lc(X,\tau) = \tau\quad\text{and}\quad \Lc(f) = \Omega(f)^*.$$

\num {\bf Separation axioms.} For a topological space $(X,\tau)$, we say that it is
\begin{itemize}
    \item[$T_0$:] if for every two distinct points $x,y\in X$ there exist an open $U\in \tau$ such that $x\in U\not\ni y$ or $x\not\in U\ni y$.
    \item[$T_1$:] if for every two distinct points $x,y\in X$ there exist an open $U\in \tau$ such that $x\in U\not\ni y$.
    \item[$T_2$:] if for every two distinct points $x,y\in X$ there exist disjoint open sets $U,V\in \tau$ separating $x$ and $y$, i.e. $x\in U\not\ni y$ and $x\not\in V\ni y$.
    \item[$T_3$:] if for each point $x\in X$ and each closed $F\subseteq X$ such that $x\notin F$ there exist two disjoint open sets separating $x$ and $F$.
    \item[$T_{3.5}$:] if for each point $x\in X$ and each closed $F\subseteq X$ such that $x\notin F$ there exist a continuous function $f\colon X\to [0,1]$ separating $x$ and $F$, i.e. $f(x) = 0$ and $f[F] = 1$.
    \item[$T_{4}$:] if for every two disjoin closed subsets of $X$ there exist two disjoint open sets separating them, or equivalently, there exists a continuous function separating them.
\end{itemize}

And we see that
$$ T_4~\&~T_1 \implies T_{3.5}~\&~T_0 \implies T_3~\&~T_0 \implies T_2 \implies T_1 \implies T_0. $$

\noindent Topological spaces satisfying $T_2$, $T_3$ and $T_0$, $T_{3.5}$ and $T_0$, or (just) $T_4$ are called, in order, \emph{Hausdorff}, \emph{regular}, \emph{completely regular}, or \emph{normal}.
The condition $T_3$ is equivalent to the condition
$$U = \bigcup \Set{ V\subseteq X | \closure V \subseteq U},\quad\text{for all open } U\in \tau.$$

Observe, $\closure V\subseteq U$ if and only if $V^*\cup U = X$ in the frame $\Omega(X)$. Define,
$$ a\rbelow b\quad\stackrel{\text{def}}{\equiv}\quad a^*\vee b = 1,$$

\noindent A frame $L$ is said to be \emph{regular} if
$$ a = \bigvee \Set{ x | x\rbelow a},$$
\noindent for all $a\in L$. Then, a space $X$ is regular if and only if the frame $\Omega(X)$ is regular.
Analogously for complete regularity, define
\begin{align*}
    a\crbelow b\quad\stackrel{\text{def}}{\equiv}\quad &\text{there exists } a_i\in L,\text{ for all } i\in \mathbb Q\cap [0,1],\text{ such that}\\
        & a_0 = a,~ a_1 = b\text{ and } a_i\rbelow a_j\text{ whenever } i<j.
\end{align*}

\noindent Then, a frame $L$ is \emph{completely regular} if
$$ a = \bigvee \Set{ x | x\crbelow a},$$

\noindent for all $a\in L$. Again, a space $X$ is completely regular if and only if the frame $\Omega(X)$ is.

Finally, a frame is said to be \emph{normal} if
$$ a\vee b = 1\quad\implies\quad \exists c\text{ such that } a\vee c = 1\text{ and }c^*\vee b = 1. $$

\noindent Similarly to topological spaces, we have: {\em \label{p:normalRegular}Any normal and regular frame is completely regular.}
\begin{center}
\parbox{0.85\linewidth}{
    (\emph{Proof.} For $x\rbelow y$, the $x^*\vee y = 1$ holds, from normality there exists a $q$, such that $x^*\vee q = 1$ and $q^*\vee y = 1$, thus $x\rbelow q\rbelow y$. Hence, by (CDC): $\Set{x | x\rbelow b} = \Set{x | x\crbelow b}$
    \qed)
}
\end{center}
\vspace{0.5em}

\begin{observation*}\label{p:rbellowProperties}\label{p:crbellowProperties} Let $\lhd\in \{\rbelow, \crbelow\}$, then
\begin{enumerate}
    \item $a'\leq a\lhd b\leq b$ implies $a'\lhd b'$,
    \item $a_1\lhd b_1$ and $a_2\lhd b_2$ implies $a_1\wedge a_2 \lhd b_1 \wedge b_2$ and $a_1\vee a_2 \lhd b_1 \vee b_2$,\text{ and}
    \item $a \lhd b$ implies $b^* \lhd a^*$.
\end{enumerate}
\end{observation*}

\num TODO spatiality and points, the functor $\Sigma$ % adjunction of $\Sigma$ and $\Omega$, Spatiality, some spatiality theorems, points!

\num A \emph{subspace} $(Y\subseteq X,\restr{\tau}{Y})$ of a topological space $(X,\tau)$ (where $\restr{\tau}{Y} = \Set{ Y\cap O | O\in \tau}$) determines the one-one inclusion (and continuous) mappings $j\colon Y\subseteq X$. The associated localic map $\Lc(j)\colon \Lc(Y)\subseteq \Lc(X)$ is one-one and its adjoint is an onto frame homomorphisms $\Omega(j)\colon \Omega(X)\to \Omega(Y)$.

% TODO better wording (starting with ``if the inclusion ...'')
Thus, for a locales $L$ and $S\subseteq L$, $S$ is said to be a \DEF{sublocale} of $L$ if the inclusion (one-one) mapping $j\colon S\subseteq L$ is a localic map and, for $s,t\in S$, $s\leq t$ whenever $j(s)\leq j(t)$.
Or equivalently, there exists an onto frame homomorphisms $j^*\colon L\to S$.

One has an another useful characterisation of sublocales, let $L$ be a frame, a subset $S\subseteq L$ is sublocale if and only if
\begin{enumerate}[(S1)]
    \item $S$ is closed under all meets, and
    \item $x\to s\in S$ for each $s\in S$ and $x\in L$.
\end{enumerate}

Denote by $\Sl(L)$ the set of all sublocales of $L$. Then, $\Sl(L)$ ordered by inclusion is a co-frame (in other words, $\Sl(L)\op$ is a frame). The empty sublocale $\emptyFrm = \{1\}$ is the least sublocale and $L$ is the greatest.

\num A sublocale is said to be \DEF{open}[ sublocale] resp. \DEF{closed}[ sublocale] if it is of the form
$$ \open(a) = \Set{ a\to x | x\in L}\quad\text{resp.}\quad \clos(c) = \upset a,$$

\noindent for some $a$. A sublocale which is both open and closed is called \emph{clopen}. An inspiration for this definition comes naturally from topological spaces. For a topological space $(X,\tau)$ and an open subset $O\in \tau$, we have the inclusion mapping
$$ j\colon (O, \Set{U\in\tau | U\subseteq O})\to (X,\tau) $$
and an onto frame homomorphisms $\Omega(j)\colon U\mapsto U\cap O$. Hence, we have the formula 
$$ \Lc(j)\colon U\mapsto O\to U,$$
for the associated localic embedding, the right adjoint to $\Omega(j)$. The sublocales $\clos(a)$ and $\open(a)$ are mutually complemented in $\Sl(L)$ ($\clos(a)\vee \open(a) = L$ and $\clos(a)\wedge \open(a) = \emptyFrm$). Moreover, we have
    \begin{alignat*}{2}
        \bigvee_i \open(a_i) &= \open(\bigvee_i a_i), &\open(a)\wedge\open(b) = \open(a\wedge b), \\
        \bigwedge_i \clos(a_i) &= \clos(\bigvee_i a_i),\quad\text{and}\quad &\clos(a)\vee\clos(b) = \clos(a\wedge b).
    \end{alignat*}

For a sublocale $S\subseteq L$, its \DEF{closure}[ of a sublocale], the least closed sublocale containing $S$, is given by the following formula
$$ \closure S = \upset (\bigwedge S). $$
From that, we immediately see that a sublocale $S\subseteq L$ is \emph{dense} (that is, $\closure S = L$) iff $0_L\in S$.

The closure of sublocales satisfies the familiar properties: $S\subseteq \closure S$, $\closure\emptyFrm = \emptyFrm$, $\closure{\closure S} = \closure S$ and $\closure S\vee \closure T = \closure{S\vee T}$; and also $\closure{\open(a)} = \clos(a^*)$.

\begin{proposition*}\label{p:preimageOfSublocales}
    Preimage of closed (resp. open) sublocale under a localic map $f$ is again a closed (resp. open). Moreover,
    $$ f^{-1}[\clos(a)] = \clos(f^*(a))\quad\text{and}\quad f^{-1}[\open(a)] = \open(f^*(a)), $$
    where $f^*$ is the left Galois adjoint to $f$.
\end{proposition*}

\num\label{p:nuclProp}\textbf{Nuclei.} Let $L$ be a frame, \DEF{nucleus} $\nu$ on $L$ is a monotone map $\nu\colon L \to L$ satisfying the following four properties:
\begin{enumerate}[(N1)]
    \item $a \leq \nu(a)$,
    \item $a \leq b$ implies $\nu(a) \leq \nu(b)$,
    \item $\nu\nu(a) = \nu(a)$, and
    \item $\nu(a \wedge b) = \nu(a) \wedge \nu(b)$.
\end{enumerate}

For a frame $L$ and a nucleus $\nu\colon L \to L$, set $S = \nu(L)$. The set $S$, together with suprema and infima defined
    $$ \bigsqcup a_i = \nu(\bigvee a_i)\quad\text{ and }\quad a \sqcap b = a \wedge b, $$

\noindent is a sublocale of $L$. Indeed, from (N4), we know that $\sqcap$ is the infimum and, from (N2), we know that $\bigsqcup$ is the supremum. Moreover, we have
$$ (\bigsqcup a_i)\sqcap b = \nu(\bigvee a_i) \wedge \nu(b) = \nu(\bigvee(a_i \wedge b)) = \bigsqcup (a_i \sqcap b).$$

\noindent Hence $\nu(L)$ is a frame, we will show that the monotone map defined as $(\nu^*\colon a \mapsto \nu(a))\colon L \to \nu(L)$ is an onto frame homomorphism. Then, we know that $\nu(L)$ is a sublocale of $L$. It is enough to show that
    $$\nu(\bigvee a_i) = \nu(\bigvee \nu(a_i)) \quad( = \bigsqcup \nu(a_i)).$$

    \noindent We have $\bigvee a_i \leq \bigvee \nu(a_i)$ by (N1) and $\nu(\bigvee a_i) \leq \nu(\bigvee \nu(a_i))$ by (N2). On the other hand $\nu(a_i) \leq \nu(\bigvee a_i)$ by (N2). Hence $\bigvee \nu(a_i) \leq \nu(\bigvee a_i)$ and $\nu(\bigvee \nu(a_i)) \leq \nu\nu(\bigvee a_i) = \nu(\bigvee a_i)$ by (N2) and (N3).

    Thus, a nuclei deteremine sublocales. One has more, there is an one-one correspondence between nuclei and sublocales.

